The Elements of Theses

### 2014-08-25 thesis/Overview.tex
update to thesis

\chapter{System Overview}
\label{chap:overview}
At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which
means no fine-grained file system metadata can be used to determine the changed data. 
Backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.  
As discussed earlier, collocating a backup service on the existing
cloud cluster avoids the extra cost to acquire a dedicated backup facility
and reduces the network bandwidth consumption in transferring the
raw data for backup. 
Figure~\ref{fig:collocated} illustrates the cluster architecture where
each physical machine runs a backup service and a distributed file system (DFS)~\cite{googlefs03,hdfs10} 
serves a backup store  for the snapshots.

\begin{figure}[htb]
    \centering
    \includegraphics[width=5in]{images/colocated-arch}
    \caption{Collocated VM Backup System.}
    \label{fig:collocated}
\end{figure}

@@

\section{Two Level Hierarchical Design of VM Metadata}
\label{overview:meta}

>>>>

\chapter{System Overview}
\label{chap:overview}
At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which
means no fine-grained file system metadata can be used to determine the changed data. 
Backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.  
As discussed earlier, collocating a backup service on the existing
cloud cluster avoids the extra cost to acquire a dedicated backup facility
and reduces the network bandwidth consumption in transferring the
raw data for backup. 
% Figure~\ref{fig:collocated} illustrates the cluster architecture where
% each physical machine runs a backup service and a distributed file system (DFS)~\cite{googlefs03,hdfs10}
% serves a backup store  for the snapshots.
Figure~\ref{fig:collocated} illustrates a converged IaaS cloud architecture
where each commodity server hosts a number of virtual machines and storage of these servers
is clustered using a distributed file system~\cite{googlefs03,hdfs10}.
Each physical machine hosts multiple virtual machines.  Every virtual machine
runs its own guest operating system and accesses virtual hard disks
stored as image files maintained by the operating system running on the
physical host.

\begin{figure}[htb]
    \centering
    \includegraphics[width=5in]{images/colocated-arch}
    \caption{VM snapshot backup running on a converged cloud cluster.}
    \label{fig:collocated}
\end{figure}

@@

\section{VM Snapshot Metadata Hierarchy}
\label{overview:meta}

### 2014-08-25 thesis/Vitae.tex
update to thesis

%{\bf Selected Publications}
\begin{vitaesection}{Publications}
%\vspace{-0.5cm}
\item Michael Daniel Agun, Wei Zhang, Tao Yang, ``Optimized Synchronous Data Deduplication for Virtual Machine Backup in Cloud Storage''. {\it To be submitted for publication}.

\item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang. ``Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud''. {\it Submitted to the 12th USENIX Conference on File and Storage Technologies (FAST '14)}.

@@

   % \item Me Myself, S. Mart, and A. Nother Advisor:
   % ``Cool Paper Title,'' In
   % {\it Proc.\ IEEE Intl.\ Conference Cool Papers 
   %      (ICCP)}, August 2000.
\vspace{0.3cm}

>>>>

%{\bf Selected Publications}
\begin{vitaesection}{Publications}
%\vspace{-0.5cm}
\item Michael Daniel Agun, Tao Yang, Wei Zhang. ``Asynchronous Source-side Deduplication for Cloud Data Backup''. {\it To be submitted for publication}.

\item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang. ``VM-Centric Snapshot Deduplication for Converged Cloud Architectures''. {\it Submitted to 2014 ACM Symposium on Cloud Computing (SoCC'14)}.

@@

\vspace{0.3cm}
